LSOA Deprevation maps

### 2021-08-09 LSOA Deprevation.Rmd
changing title

---
title: "Solent region: Test Maps"
author: "Meghan Kinglsey-Walsh"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: TRUE
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    fig_width: 5
---

@@

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Southampton LSOA Indices of dep}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")

>>>>

---
title: "LSOA Deprevation maps"
author: "Meghan Kinglsey-Walsh"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: TRUE
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    fig_width: 5
---

@@

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep$LSOA11CD <- lsoa_multidep$lsoa11cd #creating a variable with the LSOA code in the same name as in sf_data
head(lsoa_multidep)
lsoa_multidep_merged_sf <- merge(lsoa_sf_data, lsoa_multidep) #merging these
ggplot2::ggplot(lsoa_multidep_merged_sf) +
  geom_sf(aes(fill=`IMDScore`))+ # which data set has the scores?
  scale_fill_continuous(name="IMD Score", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```

#####Looking at the cities in more detail
```{r Southampton LSOA Indices of dep}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")
